---
title: "SQL injections"
author: "Cynthia Taylor, Eliana Grosof, Sam Fertig, Evans Muzulu"
date: "7/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE, message=FALSE}

databaseName = 'stackoverflow'
hostName = '127.0.0.1'
password = 'REDACTED'
userName = 'REDACTED'

```
Authentication
```{r, echo=FALSE, message=FALSE}
  library(dbplyr) 
  library(mdsr)   
  library(RMySQL)
  library(ggthemes)
  library(ggplot2)

   db <- dbConnect(RMySQL::MySQL(), 
    dbname = databaseName,
    host = hostName,
    user = userName,
    password = password)

  query <- "SELECT * FROM final_socodes"
  final_socodes <- db %>% dbGetQuery(query) %>% collect()
```
// Querying the different types of data we have
```{r, echo=FALSE, message=FALSE}

questions <- final_socodes %>% filter(type=="question")

answers <- final_socodes %>% filter(type=="answer")

everything_else <- final_socodes %>% filter(type=="everything_else")

```


Questions we can and should answer, now that we’ve been over that:
How many people who post SQL code which includes user input and at least one SQL query (a relevant question) post SQL injectable code?

```{r}

  final_socodes <- final_socodes %>% mutate(sql_injectable = as.character(sql_injectable))
  
    sql_percent <-function(dataset){
        dataset <- dataset %>% mutate(sql_injectable = as.character(sql_injectable))
        dataset <- dataset %>% filter(relevant==1) %>% group_by(type, sql_injectable) %>% summarize(count=n())
        dataset <- dataset %>% mutate(percent = count/sum(count)*100)
        return(dataset)
    }
    
    question_percent <- sql_percent(questions)
    answer_percent <- sql_percent(answers)
    everything_else_percent <- sql_percent(everything_else)
    
    
    q1 <-rbind(question_percent, answer_percent, everything_else_percent)

    write.csv(q1, "Question1.csv")

  q1_picture <-q1 %>% ggplot( aes(x=type, y=count, fill=sql_injectable)) + geom_col()  + xlab("Type") + ylab("Number of items")+ coord_flip()
  
  
  #I am supposed to have percentages here
  
  q1_picture
  

```
Of the questions that sql-injectable, how many have sql-injectable answers?
```{r, echo=FALSE, message=FALSE}
### queries
query_zero <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.relevant=1 AND x.type='question' AND x.sql_injectable=1 AND y.type='answer' AND y.sql_injectable="
query_one <- paste(query_zero,"1")

si_zero <- db %>% dbGetQuery(paste(query_zero,"0")) %>% collect()
si_one <- db %>% dbGetQuery(query_one) %>% collect()

q2 <- cbind(c('Non SQL-injectable answer', 'SQL-injectable answer'),rbind(si_zero, si_one))
#rename columns
names(q2)[1] <- 'label'
names(q2)[2] <- 'count'
write.csv(q2, "Question2.csv")
```

```{r}
### Makes a pie chart of the data in R. #######
si_zero <- as.numeric(as.character(si_zero))
si_one <- as.numeric(as.character(si_one))

slices <- c(si_zero, si_one)
labels <- c('Non SQL-injectable', 'SQL-injectable')
percent <- round(slices/sum(slices)*100)
labels <- paste(labels, paste(percent,'%', sep=""))
pie(slices, labels=labels, col = c('red', 'blue'), main='Questions with SQL-injectable code that have SQL-injectable answers')

#library(waffle)
#waffle(
#  c('SQL-injectable answer'= si_one, 'Non-SQL-injectable answer'= si_zero), rows=7)
```

Comparison of questions 1-5 in this document: https://docs.google.com/document/d/11deLxXumfRyBlbk5nSV_ili5mYtZ3y3Of1nxwhDlt_U/edit
(Just for the question)
UpSetR documentation: https://rdrr.io/cran/UpSetR/man/upset.html 
```{r, echo=FALSE, message=FALSE}
query_upset <- "SELECT sql_injectable, real_escape, bounded_user_input, prepared FROM final_socodes WHERE type='question';"
query_upset <- db %>% dbGetQuery(query_upset) %>% collect();

library(UpSetR);
upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", group.by = 'sets')
#shows empty intersections, too
#upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", empty.intersections = "on") 
```
How often do people mention that code is open to sql injection?
```{r, echo=FALSE, message=FALSE}
ms_table <- final_socodes %>% filter(relevant=="1")
ms_table <- subset(ms_table, select=c("type", "mentions_sqli"))

    ms_percent <-function(dataset){
        dataset <- dataset %>% mutate(mention_sqli = as.character(mentions_sqli))
        dataset <- dataset %>% filter(relevant==1) %>% group_by(type, mentions_sqli) %>% summarize(count=n())
        dataset <- dataset %>% mutate(percent = count/sum(count)*100)
        return(dataset)
    }
    
    q_percent <- ms_percent(questions)
    a_percent <- ms_percent(answers)
    ee_percent <- ms_percent(everything_else)
    
    
    ms_table <-rbind(q_percent, a_percent, ee_percent)

    ms_plot <- ms_table %>% ggplot( aes(x=type, y=count, fill=mentions_sqli)) + geom_bar(position="stack", stat="identity") + xlab("Type") + ylab("Number of items")
    ms_plot + theme_classic() + theme(legend.position = "none")
    
    #will make it nicer later


```

Of these people, how many think their code is secure?

```{r, echo =FALSE, message=FALSE}

# We are defining thinking that your code is secure as having at least one of these things: real_escape, bounded_user_input, prepared_statements

  
  security_codes <- final_socodes %>% filter(relevant == 1) %>% group_by(type) %>% summarise( use_re = sum(real_escape), use_bui= sum(bounded_user_input), use_prepared = sum(prepared), total=n())

security_codes <-security_codes %>% mutate(percent_re = use_re/total*100, percent_bui = use_bui/total*100, percent_prepared = use_prepared/total*100)


haha <- final_socodes %>% filter(relevant==1) %>% arrange() %>% ggplot(aes(x=type, fill=type)) + geom_bar() +
  scale_fill_brewer(palette = "Set3")
haha







```



How many people who post SQL code which includes user input and at least one SQL query (a relevant question) post SQL injectable code?
Of these people, how many think their code is secure?
Of these people, how many are explicitly looking for security advice?
Does this change the quality of the answer? Do you get good security advice on StackOverflow only when you ask for it?
Of these people, how many answers and everything_elses offer security advice?
How many offer good security advice? (as determined by the level of specificity denoted above)
How many answers/comments offering security advice clearly state what they’re suggesting and why. How many just include it in their overall answer to the question? (e.g. posting a code snippet that is not SQL-injectable, but not explicitly pointing that benefit out)
How many people who post SQL code including user input and at least one SQL query post non-SQL injectable code?
Of these people, how many think their code is secure?
Of these people, how many are explicitly looking for security advice?
Of these people, how many answers and everything_elses offer suggestions that render the original code SQL injectable?



```{r, echo=FALSE, message=FALSE}

#How many people who post SQL code which includes user input and at least one SQL query (a relevant question) post SQL injectable code?

    
  summary <- final_socodes %>% filter(relevant==1 & type=='question')  %>%  group_by(sql_injectable) %>% summarise(count = n())
  

  summary <- summary %>% mutate(percent = count/sum(count) * 100)
  
  summary %>% ggplot(aes(x= sql_injectable, y=percent, fill=sql_injectable)) + geom_col() +  scale_fill_brewer(palette = "Set3") + theme_update() + scale_color_brewer(palette = "Greys") + ggtitle("Percentages of the SQL Injectability of questions")

```
```{r, echo=FALSE, message=FALSE}

#Of these people, how many think their code is secure? I am going to classify this as someone who as at least one of these things in their code

secure <- final_socodes %>% filter(relevant==1)%>% mutate(SecurityScore = as.character(prepared + real_escape + bounded_user_input)) %>% group_by(type, sql_injectable, SecurityScore) %>% summarise(count = n()) %>% mutate(percentage = count/sum(count)*100)


secure %>% ggplot(aes(x=type, y= percentage, fill=SecurityScore)) + geom_col(position="dodge") + scale_fill_brewer(palette = "Set3") + theme_update()

```
```{r, echo=FALSE, message=FALSE}

#Of these people, how many are explicitly looking for security advice?


final_socodes %>% filter(relevant==1 & type=='question') %>% group_by(sql_injectable, mentions_sqli) %>% summarize(count=n())






```




```{r}
prepared_false_security <- final_socodes %>% filter( type=='question') %>% filter(real_escape==1 | bounded_user_input==1 | prepared==1) %>% group_by(sql_injectable) %>% summarize(count = n())


prepared_false_security <- prepared_false_security %>% mutate(percent = count/sum(count) *100)

prepared_false_security %>% ggplot(aes(x = sql_injectable, y=percent, fill=sql_injectable)) + geom_col() + scale_fill_brewer(palette="Set3")

```

```{r, echo=FALSE, message=FALSE}
non_prepared_false_security <- final_socodes %>% filter( type=='question') %>% filter(real_escape==1 | bounded_user_input==1) %>% group_by(sql_injectable) %>% summarize(count = n())


non_prepared_false_security <- non_prepared_false_security %>% mutate(percent = count/sum(count) *100)

non_prepared_false_security %>% ggplot(aes(x = sql_injectable, y=percent, fill=sql_injectable)) + geom_col() + scale_fill_brewer(palette="Set3")




```

