---
title: "SQL Injections, or StackOverflow Users: Who are they? What do they know about SQL injection? Do they know things? Let's find out."
authors: "Evans Muzulu, Eliana Grosof, Sam Fertig"
date: "7/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear db connections (in case it's maxed out). Uncomment last line to clear environment.
```{r}
all_cons <- dbListConnections(MySQL())
for(con in all_cons)
  dbDisconnect(con)
rm(list=ls())
```

Authentication
```{r, echo=FALSE, include=FALSE, message=FALSE}

library(dbplyr) 
library(mdsr)   
library(RMySQL)
library(ggthemes)
library(ggplot2)

db <- dbConnect(RMySQL::MySQL(), 
                dbname = "REDACTED",
                host = "REDACTED",
                user = "REDACTED",
                password = "REDACTED")

final_socodes <- tbl(db,"final_socodes")

```

Querying the different types of data we have
```{r, echo=FALSE, message=FALSE}

questions <- final_socodes %>% filter(type=="question")

answers <- final_socodes %>% filter(type=="answer")

everything_else <- final_socodes %>% filter(type=="everything_else")

```

Initial scripts
```{r, echo=FALSE, message=FALSE}

# Initial scripts

 pages <- final_socodes %>% summarise(num_pages = n())
  number_of_pages <- pages[1, 1]
 relevant = final_socodes %>% filter(relevant==1) %>% summarize(relevant_pages = n())
  relevant
 num_sqli_questions <- final_socodes %>% filter(type=="question" & sql_injectable==1) %>% summarize(sqli_questions = n())
  num_sqli_questions
   num_sqli_answers <- final_socodes %>% filter(type=="answer" & sql_injectable==1) %>% summarize(sqli_answers = n())
  num_sqli_answers
  num_sqli_answers <- final_socodes %>% filter(type=="everything_else" & sql_injectable==1) %>% summarize(sqli_everything = n())
  num_sqli_answers
  non_sqli_questions <- final_socodes %>% filter(type=="question" & sql_injectable==0) %>% summarize(non_sqli_questions = n())
  non_sqli_questions
  non_sqli_answers <- final_socodes %>% filter(type=="answer" & sql_injectable==0) %>% summarize(non_sqli_answers = n())
  non_sqli_answers
  non_sqli_everything <- final_socodes %>% filter(type=="everything_else" & sql_injectable==0) %>% summarize(non_sqli_everything_else = n())
  non_sqli_everything
  
sql_injectable_question <- final_socodes %>% filter(type == "question" & sql_injectable=1)
non_sql_injectable_answers <- final_socodes %>% filter(type=="answer" & sql_injectable==0)
corrected_questions <- sql_injectable_question %>% inner_join(non_sql_injectable_answers, by="id")

# Then you Count using the summarize function

```

Question time!

How many people who post SQL code--which includes user input and at least one SQL query (a relevant question)--post SQL injectable code?
```{r}

  final_socodes <- final_socodes %>% mutate(sql_injectable = as.character(sql_injectable))
  
    sql_percent <- function(dataset){
        dataset <- dataset %>% mutate(sql_injectable = as.character(sql_injectable))
        dataset <- dataset %>% filter(relevant==1) %>% group_by(type, sql_injectable) %>% summarize(count=n())
        dataset <- dataset %>% mutate(percent = count/sum(count)*100)
        return(dataset)
    }
    
    question_percent <- sql_percent(questions)
    answer_percent <- sql_percent(answers)
    everything_else_percent <- sql_percent(everything_else)
    
    
    q1 <-rbind(question_percent, answer_percent, everything_else_percent)

    write.csv(q1, "Question1.csv")

  q1_picture <-q1 %>% ggplot( aes(x=type, y=count, fill=sql_injectable)) + geom_col()  + xlab("Type") + ylab("Number of items")+ coord_flip()
  
  
  #I am supposed to have percentages here
  
  q1_picture
  
```

Of all SQL-injectable questions, how many have SQL-injectable answers?
```{r, echo=FALSE, message=FALSE}
### queries
query_zero <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.relevant=1 AND x.type='question' AND x.sql_injectable=1 AND y.type='answer' AND y.sql_injectable="
query_one <- paste(query_zero,"1")

si_zero <- db %>% dbGetQuery(paste(query_zero,"0")) %>% collect()
si_one <- db %>% dbGetQuery(query_one) %>% collect()

q2 <- cbind(c('Non SQL-injectable answer', 'SQL-injectable answer'),rbind(si_zero, si_one))
#rename columns
names(q2)[1] <- 'label'
names(q2)[2] <- 'count'
write.csv(q2, "Question2.csv")
```

```{r}
### Makes a pie chart of the data in R. #######
si_zero <- as.numeric(as.character(si_zero))
si_one <- as.numeric(as.character(si_one))

slices <- c(si_zero, si_one)
labels <- c('Non SQL-injectable', 'SQL-injectable')
percent <- round(slices/sum(slices)*100)
labels <- paste(labels, paste(percent,'%', sep=""))
pie(slices, labels=labels, col = c('green', 'red'), main='Answers to SQL-injectable Questions')

```

Comparison of questions 1-5 in this document: https://docs.google.com/document/d/11deLxXumfRyBlbk5nSV_ili5mYtZ3y3Of1nxwhDlt_U/edit
(Just for the question)
UpSetR documentation: https://rdrr.io/cran/UpSetR/man/upset.html 
BULK SECURITY CLASSIFICATION for SQL-INJECTABLE QUESTIONS
```{r, echo=FALSE, message=FALSE}
query_upset <- "SELECT sql_injectable, real_escape, bounded_user_input, prepared FROM final_socodes WHERE type='question';"
query_upset <- db %>% dbGetQuery(query_upset) %>% collect();

library(UpSetR);
upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", group.by = 'sets')

# To show empty intersections, too:
#upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", empty.intersections = "on") 

```

BULK SECURITY CLASSIFICATION for SQL-INJECTABLE ANSWERS
```{r, echo=FALSE, message=FALSE}
query_upset <- "SELECT sql_injectable, real_escape, bounded_user_input, prepared FROM final_socodes WHERE type='answer';"
query_upset <- db %>% dbGetQuery(query_upset) %>% collect();

library(UpSetR);
upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", group.by = 'sets')

# To show empty intersections, too:
#upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", empty.intersections = "on") 

```

BULK SECURITY CLASSIFICATION for SQL-INJECTABLE EVERYTHING_ELSEs
```{r, echo=FALSE, message=FALSE}
query_upset <- "SELECT sql_injectable, real_escape, bounded_user_input, prepared FROM final_socodes WHERE type='everything_else';"
query_upset <- db %>% dbGetQuery(query_upset) %>% collect();

library(UpSetR);
upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", group.by = 'sets')

# To show empty intersections, too:
#upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", empty.intersections = "on") 

```

How often do people mention SQL injection?
```{r, echo=FALSE, message=FALSE}
ms_table <- final_socodes %>% filter(relevant=="1")
ms_table <- subset(ms_table, select=c("type", "mentions_sqli"))

    ms_percent <-function(dataset){
        dataset <- dataset %>% mutate(mention_sqli = as.character(mentions_sqli))
        dataset <- dataset %>% filter(relevant==1) %>% group_by(type, mentions_sqli) %>% summarize(count=n())
        dataset <- dataset %>% mutate(percent = count/sum(count)*100)
        return(dataset)
    }
    
    q_percent <- ms_percent(questions)
    a_percent <- ms_percent(answers)
    ee_percent <- ms_percent(everything_else)
    
    
    ms_table <-rbind(q_percent, a_percent, ee_percent)

    ms_plot <- ms_table %>% ggplot( aes(x=type, y=count, fill=mentions_sqli)) + geom_bar(position="stack", stat="identity") + xlab("Type") + ylab("Number of items")
    ms_plot + theme_classic() + theme(legend.position = "none")
    
    #will make it nicer later

```

How many think their code is secure?
```{r, echo =FALSE, message=FALSE}

# We are defining thinking that your code is secure as having at least one of these things: real_escape, bounded_user_input, prepared_statements

  
  security_codes <- final_socodes %>% filter(relevant == 1) %>% group_by(type) %>% summarise( use_re = sum(real_escape), use_bui= sum(bounded_user_input), use_prepared = sum(prepared), total=n())

security_codes <-security_codes %>% mutate(percent_re = use_re/total*100, percent_bui = use_bui/total*100, percent_prepared = use_prepared/total*100)


bui <-security_codes %>% ggplot(aes(x= type, y= percent_bui))+ geom_col()  + theme_classic()

bui

re <- security_codes %>% ggplot(aes(x= type, y=percent_re)) + geom_col() + theme_classic()

re


prep <- security_codes %>% ggplot(aes(x=type, y=percent_prepared)) + geom_col() + theme_classic()


prep

```

# Of people who post SQL injectable questions, how many think their code is secure? 
# Side Q: is this a good measure of false security?
```{r}
num_false_security <- final_socodes %>% filter(sql_injectable==1 & type=='question' & (real_escape==1 || bounded_user_input==1)) %>% summarize(num_false_security = n())
  num_false_security
```

# Of these people, how many are explicitly looking for security advice?
```{r}
sec_seekers <- final_socodes %>% filter(sql_injectable==1 & type=='question' & mentions_sqli==1)
  sec_seekers
```
# Take a gander at each id.
# 29007436 --> mentions_sqli in code comment about how they use real_escape() to stop SQL_injection
# 29024361 --> mentions_sqli in code comment about how they use real_escape() (and other bui) to stop SQL_injection
# 9476097  --> asks audience to ignore SQL_injection issue, just wants advice on how to get their code to run
# 4587339  --> mentions_sqli in code comment about how they use real_escape() (and other bui) to stop SQL_injection
# 21971127 --> posted in an update to not use their code because they now realize it is vulnerable to SQL_injection
# 16019976 --> mentions_sqli in code comment about how they use real_escape() to stop SQL_injection
# 8267614  --> explicitly asks how to stop SQL injections even though they're using real_escape() and other bui

# Does this change the quality of the answer? Do you get good security advice on StackOverflow only when you ask for it?
```{r}
sec_seekers_answers <- final_socodes %>% filter(type=='answer' & (id==29007436 || id==29024361 || id==9476097 || id==4587339 || id==21971127 || id==16019976 || id==8267614))
  sec_seekers_answers
```
# Only 5 of those questions have answer. Let's take a gander.
# 29007436 --> No relevant security advice in the answer or in any comments.
# 29024361 --> No relevant security advice in the answer or in any comments. 
# 21971127 --> No relevant security advice in the answer or in any comments.
# 9476097  --> No relevant security advice in the answer or in any comments.
# 8267614  --> Relevant security advice in the answer. Doesn't suggest using prepared statements, but answers the question posed pretty thoroughly.
Above information (manually) summarized in .csv file in GitHub repo.

Of all SQL injectable questions, how many answers offer security advice?
Define: An answer counts as offering security advice if it raises the security level of the original code. Consult Security Questions doc for levels.
```{r, echo=FALSE, message=FALSE}

# Get base amounts for each query (to know percentages).
answerquery0base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=0"
answerquery1base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=1"
answerquery2base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=1"
answerquery3base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=1"

# Get answers

# Injectable questions that had ZERO sanitation--neither prepared, real_escape() nor bui--and were then recommended to use either prepared, real_escape() or bui.
answerquery0 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=0 AND y.type='answer' AND (y.prepared=1 OR y.real_escape=1 OR y.bounded_user_input=1)"

# Injectable questions that had bui--but neither prepared nor real_escape()--and were then recommended to use prepared or real_escape().
answerquery1 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=1 AND y.type='answer' AND (y.prepared=1 OR y.real_escape=1)"

# Injectable questions that had real_escape()--but not prepared--and were then recommended to use prepared.
answerquery2 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=1 AND y.type='answer' AND y.prepared=1"

# Injectable questions that used prepared statements incorrectly and were then recommended to use prepared statements correctly. 
answerquery3 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=1 AND y.type='answer' AND y.prepared=1 AND y.sql_injectable=0"

answersec0_base <- db %>% dbGetQuery(answerquery0base) %>% collect()
answersec1_base <- db %>% dbGetQuery(answerquery1base) %>% collect()
answersec2_base <- db %>% dbGetQuery(answerquery2base) %>% collect()
answersec3_base <- db %>% dbGetQuery(answerquery3base) %>% collect()

answersec0_answers <- db %>% dbGetQuery(answerquery0) %>% collect()
answersec1_answers <- db %>% dbGetQuery(answerquery1) %>% collect()
answersec2_answers <- db %>% dbGetQuery(answerquery2) %>% collect()
answersec3_answers <- db %>% dbGetQuery(answerquery3) %>% collect()

answersec0_percent <- format(round(answersec0_answers/answersec0_base*100, 2), nsmall = 2) %>% collect()
answersec1_percent <- format(round(answersec1_answers/answersec1_base*100, 2), nsmall = 2) %>% collect()
answersec2_percent <- format(round(answersec2_answers/answersec2_base*100, 2), nsmall = 2) %>% collect()
answersec3_percent <- format(round(answersec3_answers/answersec3_base*100, 2), nsmall = 2) %>% collect()

answersec0_percent
answersec1_percent
answersec2_percent
answersec3_percent

security_level<-c(0,1,2,3)
answersec_percs=c(7.07,0.86,1.28,0.00)
df<-data.frame(security_level, answersec_percs)
head(df)
blarg <- df %>% ggplot(aes(x=security_level, y=answersec_percs)) + geom_col(fill = "#FFDB6D", color = "#C4961A") + theme_classic()
print(blarg + labs(y="% of Questions with an Answer Offering Security Advice", x="Questions' Security Level", title="Security Advice Received in Answer by Security Level"))

```

Of all SQL injectable questions, how many everything_elses offer security advice?
Define: An everything_else counts as offering security advice if it raises the security level of the original code. Consult Security Questions doc for levels.
```{r, echo=FALSE, message=FALSE}

# Get base amounts for each query (to know percentages).
commentquery0base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=0"
commentquery1base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=1"
commentquery2base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=1"
commentquery3base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=1"

# Get everything_elses

# Injectable questions that had ZERO sanitation--neither prepared, real_escape() nor bui--and were then recommended to use either prepared, real_escape() or bui.
commentquery0 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=0 AND y.type='everything_else' AND (y.prepared=1 OR y.real_escape=1 OR y.bounded_user_input=1)"

# Injectable questions that had bui--but neither prepared nor real_escape()--and were then recommended to use prepared or real_escape().
commentquery1 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=1 AND y.type='everything_else' AND (y.prepared=1 OR y.real_escape=1)"

# Injectable questions that had real_escape()--but not prepared--and were then recommended to use prepared.
commentquery2 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=1 AND y.type='everything_else' AND y.prepared=1"

# Injectable questions that used prepared statements incorrectly and were then recommended to use prepared statements correctly. 
commentquery3 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=1 AND y.type='everything_else' AND y.prepared=1 AND y.sql_injectable=0"

commentsec0_base <- db %>% dbGetQuery(commentquery0base) %>% collect()
commentsec1_base <- db %>% dbGetQuery(commentquery1base) %>% collect()
commentsec2_base <- db %>% dbGetQuery(commentquery2base) %>% collect()
commentsec3_base <- db %>% dbGetQuery(commentquery3base) %>% collect()

commentsec0_answers <- db %>% dbGetQuery(commentquery0) %>% collect()
commentsec1_answers <- db %>% dbGetQuery(commentquery1) %>% collect()
commentsec2_answers <- db %>% dbGetQuery(commentquery2) %>% collect()
commentsec3_answers <- db %>% dbGetQuery(commentquery3) %>% collect()

commentsec0_percent <- format(round(commentsec0_answers/commentsec0_base*100, 2), nsmall = 2) %>% collect()
commentsec1_percent <- format(round(commentsec1_answers/commentsec1_base*100, 2), nsmall = 2) %>% collect()
commentsec2_percent <- format(round(commentsec2_answers/commentsec2_base*100, 2), nsmall = 2) %>% collect()
commentsec3_percent <- format(round(commentsec3_answers/commentsec3_base*100, 2), nsmall = 2) %>% collect()

commentsec0_percent
commentsec1_percent
commentsec2_percent
commentsec3_percent

security_level<-c(0,1,2,3)
commentsec_percs<-c(4.04,6.03,0.00,0.00)
df<-data.frame(security_level, commentsec_percs)
head(df)
blarg <- df %>% ggplot(aes(x=security_level, y=commentsec_percs)) + geom_col(fill = "#FFDB6D", color = "#C4961A") + theme_classic()
print(blarg + labs(y="% of Questions with an Everything Else Offering Security Advice", x="Questions' Security Level", title="Security Advice Received in Everything Else (by Security Level)"))

```

Answers (at least insight) to the following questions can all be found above:

  1. How many people who post SQL code which includes user input and at least one SQL query (a            relevant question) post SQL injectable code?
  
  2. Of these people, how many think their code is secure?
  
  3. Of these people, how many are explicitly looking for security advice?
  
  4. Does this change the quality of the answer? Do you get good security advice on StackOverflow         only when you ask for it?
  
  5. Of these people, how many answers and everything_elses offer security advice?
  
  6. How many offer good security advice? (as determined by the level of specificity denoted            above)
  
  7. How many answers/comments offering security advice clearly state what they’re suggesting and         why. How many just include it in their overall answer to the question? (e.g. posting a            code snippet that is not SQL-injectable, but not explicitly pointing that benefit out)


Still needing answers:

  8. How many people who post SQL code including user input and at least one SQL query post             non-SQL injectable code?

  9. Of these people, how many think their code is secure?

  10. Of these people, how many are explicitly looking for security advice?

  11. Of these people, how many answers and everything_elses offer suggestions that render the            original code SQL injectable?