---
title: "SQL Injections, or StackOverflow Users: Who are they? What do they know about
  SQL injection? Do they know things? Let's find out."
authors: Evans Muzulu, Eliana Grosof, Sam Fertig
date: "7/2/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear db connections (in case it's maxed out). Uncomment last line to clear environment.
```{r}
all_cons <- dbListConnections(MySQL())
for(con in all_cons)
  dbDisconnect(con)
rm(list=ls())
```

Authentication
```{r, echo=FALSE, include=FALSE, message=FALSE}

library(dbplyr) 
library(mdsr)   
library(RMySQL)
library(ggthemes)
library(ggplot2)

db <- dbConnect(RMySQL::MySQL(), 
                dbname = "stackoverflow",
                host = "127.0.0.1",
                user = "samfert",
                password = "^Am,a>kie&7")

final_socodes <- tbl(db,"final_socodes")

```

Querying the different types of data we have
```{r, echo=FALSE, message=FALSE}

questions <- final_socodes %>% filter(type=="question")

answers <- final_socodes %>% filter(type=="answer")

everything_else <- final_socodes %>% filter(type=="everything_else")

```

Question time!

Of all SQL-injectable questions, how many have SQL-injectable answers?
```{r, echo=FALSE, message=FALSE}
### queries
query_zero <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.relevant=1 AND x.type='question' AND x.sql_injectable=1 AND y.type='answer' AND y.sql_injectable="
query_one <- paste(query_zero,"1")

si_zero <- db %>% dbGetQuery(paste(query_zero,"0")) %>% collect()
si_one <- db %>% dbGetQuery(query_one) %>% collect()

q2 <- cbind(c('Non SQL-injectable answer', 'SQL-injectable answer'),rbind(si_zero, si_one))
#rename columns
names(q2)[1] <- 'label'
names(q2)[2] <- 'count'
write.csv(q2, "Question2.csv")
```

```{r}
### Makes a pie chart of the data in R. #######
si_zero <- as.numeric(as.character(si_zero))
si_one <- as.numeric(as.character(si_one))

slices <- c(si_zero, si_one)
labels <- c('Non SQL-injectable', 'SQL-injectable')
percent <- round(slices/sum(slices)*100)
labels <- paste(labels, paste(percent,'%', sep=""))
pie(slices, labels=labels, col = c('cyan', 'orange'), main='Answers to SQL-injectable Questions')

```

Comparison of questions 1-5 in this document: https://docs.google.com/document/d/11deLxXumfRyBlbk5nSV_ili5mYtZ3y3Of1nxwhDlt_U/edit
(Just for the question)
UpSetR documentation: https://rdrr.io/cran/UpSetR/man/upset.html 
BULK SECURITY CLASSIFICATION for QUESTIONS
```{r, echo=FALSE, message=FALSE}
query_upset <- "SELECT sql_injectable, real_escape, bounded_user_input, prepared FROM final_socodes WHERE type='question';"
query_upset <- db %>% dbGetQuery(query_upset) %>% collect();

library(UpSetR);
upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", group.by = 'sets')

# To show empty intersections, too:
#upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", empty.intersections = "on") 

```

BULK SECURITY CLASSIFICATION for ANSWERS
```{r, echo=FALSE, message=FALSE}
query_upset <- "SELECT sql_injectable, real_escape, bounded_user_input, prepared FROM final_socodes WHERE type='answer';"
query_upset <- db %>% dbGetQuery(query_upset) %>% collect();

library(UpSetR);
upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", group.by = 'sets')

# To show empty intersections, too:
#upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", empty.intersections = "on") 

```

BULK SECURITY CLASSIFICATION for EVERYTHING_ELSE
```{r, echo=FALSE, message=FALSE}
query_upset <- "SELECT sql_injectable, real_escape, bounded_user_input, prepared FROM final_socodes WHERE type='everything_else';"
query_upset <- db %>% dbGetQuery(query_upset) %>% collect();

library(UpSetR);
upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", group.by = 'sets')

# To show empty intersections, too:
#upset(query_upset, order.by="freq", main.bar.color = "#995ee1", sets.bar.color = "#995ee1", empty.intersections = "on") 

```

Of people who post SQL-injectable questions, how many think their code is secure? 
Side Q: is this a good measure of false security?
```{r}
num_false_security <- final_socodes %>% filter(sql_injectable==1 & type=='question' & (prepared==1 || real_escape==1 || bounded_user_input==1)) %>% summarize(num_false_security = n())
  num_false_security
```

Of people who post SQL injectable code (question, answer, or everything else), how many think their code is secure? 
```{r,echo=FALSE,message=FALSE}

false_promises<-final_socodes %>% filter(sql_injectable==1 & code_snippet==1 & (prepared==1 ||real_escape==1 || bounded_user_input==1)) %>% group_by(type) %>% summarize(use_re=sum(real_escape), use_bui=sum(bounded_user_input), use_prepared=sum(prepared), total=n())

false_promises<-false_promises %>% mutate(percent_re=use_re/total*100, percent_bui=use_bui/total*100, percent_prepared=use_prepared/total*100)

types <- c("question", "answer", "everything_else")

bui_mistaken<-false_promises %>% ggplot(aes(x=reorder(type, -percent_bui), y=percent_bui)) + geom_col(fill = "#FFDB6D", color = "#C4961A",width = 0.7) + theme_clean() + scale_x_discrete(limits = types)

re_mistaken<-false_promises %>% ggplot(aes(x=reorder(type, -percent_re), y=percent_re)) + geom_col(fill = "#FFDB6D", color = "#C4961A",width = 0.7) + theme_clean() + scale_x_discrete(limits = types)

prep_mistaken<-false_promises %>% ggplot(aes(x=reorder(type, -percent_prepared), y=percent_prepared)) + geom_col(fill = "#FFDB6D", color = "#C4961A",width = 0.7) + theme_clean() + scale_x_discrete(limits = types)

print(bui_mistaken + labs(y="% using bui", x="type", title="SQL Injectable Code using Bounded User Input"))
print(re_mistaken + labs(y="% using re", x="type", title="SQL Injectable Code using real_escape_string()"))
print(prep_mistaken + labs(y="% using prep", x="type", title="SQL Injectable Code using Prepared Statments"))

```

# Of these people, how many are explicitly looking for security advice?
```{r,echo=FALSE,message=FALSE}
sec_seekers <- final_socodes %>% filter(sql_injectable==1 & type=='question' & mentions_sqli==1)
  sec_seekers
```
Take a gander at each id.
29007436 --> mentions_sqli in code comment about how they use real_escape() to stop SQL_injection
29024361 --> mentions_sqli in code comment about how they use real_escape() (and other bui) to stop SQL_injection
9476097  --> asks audience to ignore SQL_injection issue, just wants advice on how to get their code to run
4587339  --> mentions_sqli in code comment about how they use real_escape() (and other bui) to stop SQL_injection
21971127 --> posted in an update to not use their code because they now realize it is vulnerable to SQL_injection
16019976 --> mentions_sqli in code comment about how they use real_escape() to stop SQL_injection
8267614  --> explicitly asks how to stop SQL injections even though they're using real_escape() and other bui

Does this change the quality of the answer? Do you get good security advice on StackOverflow only when you ask for it?
```{r,echo=FALSE,message=FALSE}
sec_seekers_answers <- final_socodes %>% filter(type=='answer' & (id==29007436 || id==29024361 || id==9476097 || id==4587339 || id==21971127 || id==16019976 || id==8267614))
  sec_seekers_answers
```
Only 5 of those questions have answers. Let's take a gander.
29007436 --> No relevant security advice in the answer or in any comments.
29024361 --> No relevant security advice in the answer or in any comments. 
21971127 --> No relevant security advice in the answer or in any comments.
9476097  --> No relevant security advice in the answer or in any comments.
8267614  --> Relevant security advice in the answer. Doesn't suggest using prepared statements, but answers the question posed pretty thoroughly.
Above information (manually) summarized in .csv file in GitHub repo. Title = 'msqli questions.csv'

Of all SQL injectable questions, how many answers offer security advice?
Define: An answer counts as offering security advice if it raises the security level of the original code. Consult Security Questions doc for levels.
```{r, echo=FALSE, message=FALSE}

# Get base amounts for each query (to know percentages).
answerquery0base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=0"
answerquery1base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=1"
answerquery2base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=1"
answerquery3base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=1"

# Get answers

# Injectable questions that had ZERO sanitation--neither prepared, real_escape() nor bui--and were then recommended to use either prepared, real_escape() or bui.
answerquery0 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=0 AND y.type='answer' AND (y.prepared=1 OR y.real_escape=1 OR y.bounded_user_input=1)"

# Injectable questions that had bui--but neither prepared nor real_escape()--and were then recommended to use prepared or real_escape().
answerquery1 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=1 AND y.type='answer' AND (y.prepared=1 OR y.real_escape=1)"

# Injectable questions that had real_escape()--but not prepared--and were then recommended to use prepared.
answerquery2 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=1 AND y.type='answer' AND y.prepared=1"

# Injectable questions that used prepared statements incorrectly and were then recommended to use prepared statements correctly. 
answerquery3 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=1 AND y.type='answer' AND y.prepared=1 AND y.sql_injectable=0"

answersec0_base <- db %>% dbGetQuery(answerquery0base) %>% collect()
answersec1_base <- db %>% dbGetQuery(answerquery1base) %>% collect()
answersec2_base <- db %>% dbGetQuery(answerquery2base) %>% collect()
answersec3_base <- db %>% dbGetQuery(answerquery3base) %>% collect()

answersec0_answers <- db %>% dbGetQuery(answerquery0) %>% collect()
answersec1_answers <- db %>% dbGetQuery(answerquery1) %>% collect()
answersec2_answers <- db %>% dbGetQuery(answerquery2) %>% collect()
answersec3_answers <- db %>% dbGetQuery(answerquery3) %>% collect()

answersec0_percent <- format(round(answersec0_answers/answersec0_base*100, 2), nsmall = 2) %>% collect()
answersec1_percent <- format(round(answersec1_answers/answersec1_base*100, 2), nsmall = 2) %>% collect()
answersec2_percent <- format(round(answersec2_answers/answersec2_base*100, 2), nsmall = 2) %>% collect()
answersec3_percent <- format(round(answersec3_answers/answersec3_base*100, 2), nsmall = 2) %>% collect()

answersec0_percent
answersec1_percent
answersec2_percent
answersec3_percent

security_level<-c(0,1,2,3)
answersec_percs=c(7.07,0.86,1.28,0.00)
df<-data.frame(security_level, answersec_percs)
head(df)
blarg <- df %>% ggplot(aes(x=security_level, y=answersec_percs)) + geom_col(fill = "#FFDB6D", color = "#C4961A") + theme_classic()
print(blarg + labs(y="%", x="security level", title="Percent of SQLI Questions with an Answer Offering Security Advice,\n by Question's Security Level"))

```

Of all SQL injectable questions, how many everything_elses offer security advice?
Define: An everything_else counts as offering security advice if it raises the security level of the original code. Consult Security Questions doc for levels.
```{r, echo=FALSE, message=FALSE}

# Get base amounts for each query (to know percentages).
commentquery0base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=0"
commentquery1base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=1"
commentquery2base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=1"
commentquery3base <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=1"

# Get everything_elses

# Injectable questions that had ZERO sanitation--neither prepared, real_escape() nor bui--and were then recommended to use either prepared, real_escape() or bui.
commentquery0 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=0 AND y.type='everything_else' AND (y.prepared=1 OR y.real_escape=1 OR y.bounded_user_input=1)"

# Injectable questions that had bui--but neither prepared nor real_escape()--and were then recommended to use prepared or real_escape().
commentquery1 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=0 AND x.bounded_user_input=1 AND y.type='everything_else' AND (y.prepared=1 OR y.real_escape=1)"

# Injectable questions that had real_escape()--but not prepared--and were then recommended to use prepared.
commentquery2 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=0 AND x.real_escape=1 AND y.type='everything_else' AND y.prepared=1"

# Injectable questions that used prepared statements incorrectly and were then recommended to use prepared statements correctly. 
commentquery3 <- "SELECT COUNT(x.id) FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=1 AND x.prepared=1 AND y.type='everything_else' AND y.prepared=1 AND y.sql_injectable=0"

commentsec0_base <- db %>% dbGetQuery(commentquery0base) %>% collect()
commentsec1_base <- db %>% dbGetQuery(commentquery1base) %>% collect()
commentsec2_base <- db %>% dbGetQuery(commentquery2base) %>% collect()
commentsec3_base <- db %>% dbGetQuery(commentquery3base) %>% collect()

commentsec0_answers <- db %>% dbGetQuery(commentquery0) %>% collect()
commentsec1_answers <- db %>% dbGetQuery(commentquery1) %>% collect()
commentsec2_answers <- db %>% dbGetQuery(commentquery2) %>% collect()
commentsec3_answers <- db %>% dbGetQuery(commentquery3) %>% collect()

commentsec0_percent <- format(round(commentsec0_answers/commentsec0_base*100, 2), nsmall = 2) %>% collect()
commentsec1_percent <- format(round(commentsec1_answers/commentsec1_base*100, 2), nsmall = 2) %>% collect()
commentsec2_percent <- format(round(commentsec2_answers/commentsec2_base*100, 2), nsmall = 2) %>% collect()
commentsec3_percent <- format(round(commentsec3_answers/commentsec3_base*100, 2), nsmall = 2) %>% collect()

commentsec0_percent
commentsec1_percent
commentsec2_percent
commentsec3_percent

security_level<-c(0,1,2,3)
commentsec_percs<-c(4.04,6.03,0.00,0.00)
df<-data.frame(security_level, commentsec_percs)
head(df)
blarg <- df %>% ggplot(aes(x=security_level, y=commentsec_percs)) + geom_col(fill = "#FFDB6D", color = "#C4961A") + theme_classic()
print(blarg + labs(y="%", x="security level", title="Percent of SQLI Questions with an EE Offering Security Advice,\n by Question's Security Level"))

```

Answers (at least insight) to the following questions can all be found above:

  1. How many people who post SQL code which includes user input and at least one SQL query (a relevant question) post SQL injectable code?
  
  2. Of these people, how many think their code is secure?
  
  3. Of these people, how many are explicitly looking for security advice?
  
  4. Does this change the quality of the answer? Do you get good security advice on StackOverflow only when you ask for it?
  
  5. Of these people, how many answers and everything_elses offer security advice?
  
  6. How many offer good security advice? (as determined by the level of specificity denoted above)
  
  7. How many answers/comments offering security advice clearly state what they’re suggesting and why. How many just include it in their overall answer to the question? (e.g. posting a code snippet that is not SQL-injectable, but not explicitly pointing that benefit out)


Still needing answers:

  8. How many people who post SQL code including user input and at least one SQL query post non-SQL injectable code?

  9. Of these people, how many think their code is secure?

  10. Of these people, how many are explicitly looking for security advice?

  11. Of these people, how many answers and everything_elses offer suggestions that render the original code SQL injectable?
  

How many people who post SQL code including user input and at least one SQL query post non-SQL injectable code?
```{r, echo=FALSE, message=FALSE}
non_sqli_questions <- final_socodes %>% filter(type=="question" & sql_injectable==0) %>% summarize(non_sqli_questions = n())
non_sqli_questions
```

Of these people, how many think their code is secure?
Of these people, how many are explicitly looking for security advice?
```{r, echo=FALSE, message=FALSE}
secure_and_rightly_so <- final_socodes %>% filter(type=="question" & sql_injectable==0 & mentions_sqli==1) %>% summarize(non_sqli_questions = n())
secure_and_rightly_so
```
Presumably, because there are no non SQL-injectable questions that mention injection, none of these people are asking for security advice. Perhaps this means that all of them know their code is secure.

Of these people, how many answers and everything_elses offer suggestions that render the original code SQL injectable?
```{r, echo=FALSE, message=FALSE}

query_for_stupid <- "SELECT x.id FROM final_socodes x INNER JOIN final_socodes y ON y.id = x.id WHERE x.type='question' AND x.sql_injectable=0 AND ( (y.type='answer' OR y.type='everything_else') AND y.sql_injectable=1)"

idiot_suggestions <- db %>% dbGetQuery(query_for_stupid) %>% collect()
idiot_suggestions

```
# Takeaway: there is not a single non-SQL-injectable question with a SQL injectable answer or comment.

(!) Data sorted by year

All posts download, the year they are from
```{sql connection=db, output.var=postpost}
SELECT
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
    WHEN CreationDate LIKE '2017%' THEN '2017'
    WHEN CreationDate LIKE '2018%' THEN '2018'
  END AS 'Year'
, COUNT(*) AS 'QuestionCount'
FROM posts
GROUP BY 
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
    WHEN CreationDate LIKE '2017%' THEN '2017'
    WHEN CreationDate LIKE '2018%' THEN '2018'
  END

```

Line/dot plot -- posts by year
```{r}
postpost
library(ggplot2)
ggplot(postpost, aes(x=Year,y=QuestionCount)) + 
  geom_line(aes(group=1), colour="#FF9933") +
  geom_point(size=1, colour="#6699FF") +
  xlab("Year") +
  ylab("Question Count") +
  ggtitle("Pages Downloaded by Year Posted")
```


All sql-tagged pages available, the year they are from
```{sql connection=db, output.var=allpage_distribution}
SELECT
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
    WHEN CreationDate LIKE '2017%' THEN '2017'
    WHEN CreationDate LIKE '2018%' THEN '2018'
  END AS 'Year'
, COUNT(*) AS 'QuestionCount'
FROM sql_posts
GROUP BY 
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
    WHEN CreationDate LIKE '2017%' THEN '2017'
    WHEN CreationDate LIKE '2018%' THEN '2018'
  END

```

Line/dot plot -- pages by year
```{r}
allpage_distribution
library(ggplot2)
ggplot(allpage_distribution, aes(x=Year,y=QuestionCount)) + 
  geom_line(aes(group=1), colour="#FF9933") +
  geom_point(size=1, colour="#6699FF") +
  xlab("Year") +
  ylab("Question Count") +
  ggtitle("Pages Downloaded by Year Posted")
```


The pages we coded, the year they are from
```{sql connection=db, output.var=annual_query}
SELECT
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
  END AS 'Year'
, COUNT(*) AS 'QuestionCount'
FROM sql_posts x INNER JOIN final_socodes y ON y.id=x.id WHERE type='question'
GROUP BY 
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
  END

```

Line/dot plot -- coded pages by year
```{r}
annual_query
library(ggplot2)
ggplot(annual_query, aes(x=Year,y=QuestionCount)) + 
  geom_line(aes(group=1), colour="#FF9933") +
  geom_point(size=1, colour="#6699FF") +
  xlab("Year") +
  ylab("Question Count") +
  ggtitle("Pages Coded by Year Posted")
```

The SQL-injectable questions we coded, the year they are from
```{sql connection=db, output.var=sqliQ_peryear}
SELECT
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
  END AS 'Year'
, COUNT(*) AS 'QuestionCount'
FROM sql_posts x INNER JOIN final_socodes y ON y.id=x.id WHERE y.type='question' AND y.sql_injectable=1
GROUP BY 
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
  END

```

Line/dot plot -- SQLI questions by year
```{r}
sqliQ_peryear
library(ggplot2)
ggplot(sqliQ_peryear, aes(x=Year,y=QuestionCount)) + 
  geom_line(aes(group=1), colour="#FF9933") +
  geom_point(size=1, colour="#6699FF") +
  xlab("Year") +
  ylab("Question Count") +
  ggtitle("SQL Injectable Questions by Year Posted")
```

How many SQL injectable questions were given any sort of security advice (same criteria as in previous monster question) each year?
```{sql connection=db, output.var=advice_peryear}
SELECT
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
  END AS 'Year'
  , COUNT(*) AS 'QuestionCount'
FROM sql_posts x INNER JOIN final_socodes y ON y.id=x.id INNER JOIN final_socodes z WHERE y.id=z.id AND y.type='question' AND y.sql_injectable=1 AND 
((y.prepared=0 AND y.real_escape=0 AND y.bounded_user_input=0 AND z.type!='question' AND (z.prepared=1 OR z.real_escape=1 OR z.bounded_user_input=1)) 
OR 
(y.prepared=0 AND y.real_escape=0 AND y.bounded_user_input=1 AND z.type!='question' AND (z.prepared=1 OR z.real_escape=1)) OR (y.prepared=0 AND y.real_escape=0 AND y.bounded_user_input=1 AND z.type!='question' AND (z.prepared=1 OR z.real_escape=1)) 
OR 
(y.prepared=0 AND y.real_escape=1 AND z.type!='question' AND z.prepared=1) OR (y.prepared=1 AND z.type!='question' AND z.sql_injectable=1))
GROUP BY 
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
  END

```

```{r,echo=FALSE,message=FALSE}
advice_peryear
library(ggplot2)
ggplot(advice_peryear, aes(x=Year,y=QuestionCount)) + 
  geom_line(aes(group=1), colour="#000099") +
  geom_point(size=1, colour="#CC0000") +
  xlab("Year") +
  ylab("Question Count") +
  ggtitle("Security Advice (any) by Year Posted")
```

How many SQL injectable questions were given good security advice (prepared statements) each year?
```{sql connection=db, output.var=prepadvice_peryear}
SELECT
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
  END AS 'Year'
  , COUNT(*) AS 'QuestionCount'
FROM sql_posts x INNER JOIN final_socodes y ON y.id=x.id INNER JOIN final_socodes z WHERE y.id=z.id AND (y.type='question' AND y.sql_injectable=1) AND ((z.type='answer' OR z.type='everything_else') AND z.sql_injectable=0)
GROUP BY 
  CASE
    WHEN CreationDate LIKE '2008%' THEN '2008'
    WHEN CreationDate LIKE '2009%' THEN '2009'
    WHEN CreationDate LIKE '2010%' THEN '2010'
    WHEN CreationDate LIKE '2011%' THEN '2011'
    WHEN CreationDate LIKE '2012%' THEN '2012'
    WHEN CreationDate LIKE '2013%' THEN '2013'
    WHEN CreationDate LIKE '2014%' THEN '2014'
    WHEN CreationDate LIKE '2015%' THEN '2015'
    WHEN CreationDate LIKE '2016%' THEN '2016'
  END

```

```{r,echo=FALSE,message=FALSE}
prepadvice_peryear
library(ggplot2)
ggplot(prepadvice_peryear, aes(x=Year,y=QuestionCount)) + 
  geom_line(aes(group=1), colour="#000099") +
  geom_point(size=1, colour="#CC0000") +
  xlab("Year") +
  ylab("Question Count") +
  ggtitle("Security Advice (good) by Year Posted")
```

All lines on same graph
```{r,echo=FALSE,message=FALSE}

all4one<-allpage_distribution
all4one<-all4one %>% rename(`Questions Downloaded`=QuestionCount)

all4one<-merge(all4one, annual_query[, c("Year","QuestionCount")],by="Year",all.x=TRUE)

#all4one<-annual_query
all4one<-all4one %>% rename(`Questions Coded`=QuestionCount)

all4one<-merge(all4one, sqliQ_peryear[, c("Year","QuestionCount")],by="Year",all.x=TRUE)
all4one<-all4one %>% rename(`SQL Injectable Questions`=QuestionCount)

all4one<-merge(all4one,advice_peryear[, c("Year","QuestionCount")],by="Year", all.x=TRUE)
all4one<-all4one %>% rename(`Security Advice`=QuestionCount)

all4one<-merge(all4one,prepadvice_peryear[, c("Year","QuestionCount")],by="Year", all.x=TRUE)
all4one<-all4one %>% rename(`Good Security Advice`=QuestionCount)

colnames(all4one) = c("year", "all_questions", "coded_questions", "sqli_questions", "security_any", "security_good")
all4one[is.na(all4one)] <- 0
all4one

library(ggplot2)
theme_set(theme_minimal())

# Data preparation
library("tidyverse")
df <- all4one %>%
  select(`year`,`coded_questions`,`sqli_questions`,`security_any`,`security_good`) %>%
  gather(key = "variable", value = "count", -year)
head(df)

#reorder legend (I don't like the default)
df$variable <- factor(df$variable, levels = c("coded_questions","sqli_questions", "security_any", "security_good"))

library(hrbrthemes)
library(viridis)
library(ggsci)

# Visualization
ggplot(df, aes(x = year, y = count)) + 
  geom_line(aes(group=variable,color=variable, linetype=variable)) +
  scale_fill_jco() +
  theme_hc() +
  theme(legend.title=element_blank(),legend.position="right")

  #labels=c("Questions", "SQL injectable questions", "Security advice offered (any)", "Security advice offered (good)")

# Dark theme
# ggplot(df, aes(x = year, y = count)) + 
#   geom_line(aes(group=variable,color = variable, linetype = variable)) +
#   theme_dark() +   
#   scale_color_tron()+
#   scale_fill_tron()+
#   theme_dark() +
#   theme(
#     panel.background = element_rect(fill = "#2D2D2D"),
#     legend.key = element_rect(fill = "#2D2D2D")   
#     )

```

(!) Linear regression models 
Quick documentation:
To specify predictor variables:         model <- lm(y ~ variable + variable + ... + variable, data = <table>)
To use all predictors in the data set:  model <- lm(y ~., data = <table>)
To use all predictors except one:       model <- lm(y ~. -variable, data = <table>)

Outcome variable: coded_questions


Outcome variable: sqli_questions
```{r,echo=FALSE,message=FALSE}

#outcome variable: sqli_questions. predictor variables: all.
sqli_v_all <- lm(`sqli_questions`~coded_questions+security_any+security_good,data=all4one) 

#estimate beta coefficients and associated t-statistic p-values. AKA, what's significant
summary(sqli_v_all)$coefficient 
# Result: only all_questions is significant. 

#update model.
#outcome variable: sqli_questions. predictor variable: all_questions.
sqli_model <- lm(`sqli_questions`~coded_questions,data=all4one) 
summary(sqli_model)

# p-value of F-statistic: 6.02e-07 --> highly significant.

# With a 1,000 all_questions increase, holding all other predictors constant, we can expect an increase of 0.917*1000 = 917 sqli_questions, on average.

# Final model equation --> sqli_questions = -0.647 + 0.917*all_questions

#get confidence interval
confint(sqli_model) #confidence interval --> 97.5%

#assess model accuracy
sqli_adjR2 <- 0.9855 #adjusted R-squared: 0.9855
# “98.5% of the variance in the measure of sqli_questions can be predicted by all_questions"

sqli_RSE <- sigma(sqli_model)/mean(all4one$sqli_questions) 
# sqli_RSE: 0.0987529 --> 9% error rate

# CONCLUSION
# sqli_questions v. all_questions: highly significant.

```

Outcome variable: security_any
```{r,echo=FALSE,message=FALSE}

#outcome variable: security_any. predictor variables: all.
sqli_v_all <- lm(`sqli_questions`~coded_questions+security_any+security_good,data=all4one) 

#estimate beta coefficients and associated t-statistic p-values. AKA, what's significant
summary(sqli_v_all)$coefficient 
# Result: only sqli_questions is even close to significant. 

#update model.
#outcome variable: security_any. predictor variable: sqli_questions.
anysec_model <- lm(`security_any`~sqli_questions,data=all4one) 
summary(anysec_model)

# p-value of F-statistic: 6.02e-07 --> highly significant.

# With a 1,000 `sqli_questions` increase, holding all other predictors constant, we can expect an increase of 0.284*1000 = 284 security_any, on average.


# Final model equation --> security_any = security_any = 0.049 + 0.284*all_questions

#get confidence interval
confint(anysec_model) #confidence interval --> 97.5%

#assess model accuracy
anysec_adjR2 <- 0.7433 #adjusted R-squared: 0.7433
# “74.3% of the variance in the measure of security_any can be predicted by sqli_questions"

anysec_RSE <- sigma(sqli_model)/mean(all4one$sqli_questions) 
# anysec_RSE: 0.466729 --> 46% error rate

# CONCLUSION
# anysec_questions v. sqli_questions: significant, but massive error rate.

```

security_good
```{r,echo=FALSE,message=FALSE}

goodsec_v_all <- lm(`security_good`~all_questions+sqli_questions+security_any,data=all4one) #outcome variable: security_good. predictor variables: all.
summary(goodsec_v_all)$coefficient #estimate beta coefficients and associated t-statistic p-values. AKA, what's significant

# 
# # Result: sqli_questions is the most significant. Update model.
# anysec_model <- lm(`security_any`~sqli_questions,data=all4one) #outcome: security_any. predictor: sqli_questions.
# # summary(anysec_model)$coefficients
# # p-value of F-statistic:  --> highly significant.
# 
# summary(anysec_model) #estimate = 
# 
# 
# # Final model equation --> 
# #confint(anysec_model) #confidence interval --> 97.5%
# 
# #Assess model accuracy
# #anysec_adjR2 <- 0.7433 #adjusted R-squared: 0.7433
# #“74.3% of the variance in the measure of security_any can be predicted by sqli_questions"
# anysec_RSE <- sigma(anysec_model)/mean(all4one$security_any) #sqli_RSE: 0.466729 --> 46% error rate
# anysec_RSE
# security_any v. sqli_questions: highly significant.

```

(!) Voting stuff

```{r,echo=FALSE,message=FALSE}

votes <- read.csv(file = 'pdVotes.csv')
votes<-votes %>% rename(`id`=X)
votes
big_table <- questions
big_table
big_table<-merge(big_table,votes[, c("id","Qvote","Avote")],by="id", all.x=TRUE)
big_table


```

